Constraining the Interiors of Asteroids Through Close Encounters

### 2022-04-20 paper/main.tex
Updated Updated uncertainty model

\begin{figure*}
  \centering
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-lumpy.pdf}

  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.33\textwidth}

@@

\begin{figure*}
  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr12.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr13.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr23.pdf}

  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-ab.pdf}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.33\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/sym-ell-lumpy.pdf}

  \includegraphics[width=0.33\textwidth]{figs/db-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/db-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/db-lumpy.pdf}

  \includegraphics[width=0.33\textwidth]{figs/tet-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/tet-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/tet-lumpy.pdf}
  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid. The asteroid shapes are, from top to bottom, the reference symmetric asteroid, the dumbbell model, and a tetrahedron. Density is normalized so that mean density is one. The same distance scale is used in all figures.}
  \label{fig:uniform-density}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.33\textwidth]{figs/in-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/in-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/in-lumpy.pdf}

  \includegraphics[width=0.33\textwidth]{figs/out-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/out-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/out-lumpy.pdf}\

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.33\textwidth]{figs/blob-likelihood.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/blob-harmonic.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/blob-lumpy.pdf}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-lumpy.pdf}

  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}

@@

\begin{figure*}
  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr12.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr13.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr23.pdf}

  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-ab.pdf}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/sym-ell-lumpy.pdf}

  \includegraphics[width=0.3\textwidth]{figs/db-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/db-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/db-lumpy.pdf}

  \includegraphics[width=0.3\textwidth]{figs/tet-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/tet-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/tet-lumpy.pdf}
  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid. The asteroid shapes are, from top to bottom, the reference symmetric asteroid, the dumbbell model, and a tetrahedron. Density is normalized so that mean density is one. The same distance scale is used in all figures.}
  \label{fig:uniform-density}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/in-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/in-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/in-lumpy.pdf}

  \includegraphics[width=0.3\textwidth]{figs/out-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/out-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/out-lumpy.pdf}\

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.3\textwidth]{figs/blob-likelihood.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/blob-harmonic.pdf}\hfill
  \includegraphics[width=0.3\textwidth]{figs/blob-lumpy.pdf}
